---
title: "p8015_hw1_ajt2206"
author: "Andy Turner"
date: "2023-09-18"
output: github_document
---

# Problem 1

Loading package and data for Problem 1
```{r}
library("moderndive")
library("tidyverse")
data("early_january_weather")
```

Defining temp as the temp variable within the early_january_weather dataset. 
```{r}
temp<- early_january_weather$temp
```

**Description of Variables**

1. The variables are as follows `r names(early_january_weather)`.

1. There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

1. The mean temperature is `r round(mean(temp), digits=2)` degrees Fahrenheit.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + 
  geom_point() +
  labs(title="Scatterplot of Time_hour vs. Temperature")
```

**Patterns in the data**

* At higher temperatures, humidity is also higher.

* The temperature increased overall through the observed period before dropping quickly around January 14th. 

**Saving Scatterplot to Github**
```{r}
ggsave("hw1_scatterplot.git", plot= last_plot())ggplot(plot_df, aes(x = x, y = y)) + geom_point()
```

