---
title: "p8015_hw1_ajt2206"
author: "Andy Turner"
date: "2023-09-18"
output: github_document
---

# Problem 1

Loading package and data for Problem 1
```{r}
library("moderndive")
library("tidyverse")
data("early_january_weather")
```

Defining temp as the temp variable within the early_january_weather dataset. 
```{r}
temp<- pull(early_january_weather,temp)
```

**Description of Variables and Dataset**

1. This dataset provides hourly meterological data for LGA, JFK, and EWR for the month of January 2013. 

1. The variables are as follows `r names(early_january_weather)`. 

1. Key variables are defined as the follolwing. temp: Temperature in F. humid: relative humidity. time_hour: Date and hour of the recording as a POSIXct date.

1. There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

1. The mean temperature is `r round(mean(temp), digits=2)` degrees Fahrenheit.

**Plotting temp vs. time_hour**
```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + 
  geom_point() +
  labs(title="Scatterplot of Time_hour vs. Temperature")
```

**Patterns in the data**

* From the graph, we can see that temperature appears to generally increase through the week of observations before dropping quickly around January 14th. 

* There were many fluctuations in temperature. Fluctuations in temperature likely occurred throughout the day with higher temperatures during the day and lower temperatures during the night. 

**Saving Scatterplot to Github**
```{r}
ggsave("hw1_scatterplot.png", plot= last_plot(), width=6, height=4, dpi = 300)
```

# Problem 2

Creating a data frame & pulling out variables from within the data frame
```{r}
hw2_df= 
  tibble(
    ran_samp = rnorm(10),
    log_vec = ran_samp>0,
    char_vec = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
    fact_vec= factor(rep(c("Level 1", "Level 2", "Level 3"), times= c(4, 3, 3)))
  )
                     

ran_samp <- pull(hw2_df,ran_samp)
log_vec <- pull(hw2_df,log_vec)
char_vec <- pull(hw2_df,char_vec)
fact_vec <- pull(hw2_df,fact_vec)
```

Running means on the 4 variables:
```{r}
mean(ran_samp)
mean(log_vec)
mean(char_vec)
mean(fact_vec)
```

Mean Works: 

* Random Sample 

* Logical Vector

Mean Does Not Work:

* Character Vector 

* Factor Vector


**Attempting to convert logical, character, and factor vectors to numeric**
```{r}
as.numeric(log_vec)
as.numeric(char_vec)
as.numeric(fact_vec)
```
**Outcome**
Logical Vector and Factor Vector were both converted to Numeric. Character Vector was converted to numeric; however, there was a warning message that this occurred via coercion. All the characters were converted to NAs. 

**Why**
The logical vector we created is based off a True or False which can easily be converted to a binary number. Likewise the Factor Vector exists in three levels which can also be converted from the level to a number (1 through 3). The character vector however does not have a clear way to convert to a numeric which is why the system warns that the character vector was converted via coercion. 

**Correspondence with attempting to take the Mean** 
Overall yes, transforming our data to numeric does partially explain what happened when we tried to take the mean. For the logical vector, I could both calculate a mean and convert it to numeric easily. For the character vector, I could not calculate a mean and it was difficult to convert to numeric. The factor vector is more mixed: I could not take a mean; however, I could convert the data into numeric easily. The Categorical Data makes it where the system cannot run a mean since the data could be in Nominal Categories. 