---
title: "p8015_hw1_ajt2206"
author: "Andy Turner"
date: "2023-09-18"
output: github_document
---

# Problem 1

Loading package and data for Problem 1
```{r}
library("moderndive")
library("tidyverse")
data("early_january_weather")
```

Defining temp as the temp variable within the early_january_weather dataset. 
```{r}
temp<- early_january_weather$temp
```

**Description of Variables and Dataset**

1. This dataset provides hourly meterological data for LGA, JFK, and EWR for the month of January 2013. 

1. The variables are as follows `r names(early_january_weather)`. 

1. Key variables are defined as the follolwing. temp: Temperature in F. humid: relative humidity. time_hour: Date and hour of the recording as a POSIXct date.

1. There are `r nrow(early_january_weather)` rows and `r ncol(early_january_weather)` columns.

1. The mean temperature is `r round(mean(temp), digits=2)` degrees Fahrenheit.

```{r}
ggplot(early_january_weather, aes(x = time_hour, y = temp, color=humid)) + 
  geom_point() +
  labs(title="Scatterplot of Time_hour vs. Temperature")
```

**Patterns in the data**

* At higher temperatures, humidity is also higher.

* The temperature increased overall through the observed period before dropping quickly around January 14th. 

**Saving Scatterplot to Github**
```{r}
ggsave("hw1_scatterplot.png", plot= last_plot(), width=6, height=4, dpi = 300)
```

# Problem 2

Creating a data frame: 
```{r}
hw2_df= 
  tibble(
    ran_samp<- rnorm(10),
    log_vec<- ran_samp > 0,
    char_vec<- c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
    fact_vec<- factor(rep(c("Level 1", "Level 2", "Level 3"), times= c(4, 3, 3)))
  )


```



